TGI-spine

### 2022-04-19 analysis/tgispine_hypotheses.Rmd
normalising the VAS data by maximum values, then using these data toinform the simulation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)

@@

## Simulate results for one participant
```{r}
simulate_subj <- function(subid) {
trialN = 9
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:50,1), sd=5)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=5)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:70,1), sd=15)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)

# Burning ratings: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:60,1), sd=15)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:70,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:60,1), sd=15)
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)

@@

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:60) {
  df <- simulate_subj(i)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

## H1
names(within)[7] <- 'within'
names(across)[7] <- 'across'
# merge
H1_df <- merge(within, across, by = c('id','cold_location','stimuli','quality'))
# difference
H1_df$diff <- H1_df$within - H1_df$across

H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(truncnorm)

@@

## Simulate results for one participant
```{r}
simulate_subj <- function(subid, llim, ulim) {
trialN = 10
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# The following intervals and mean can be changed to reflect hypotheses
# using normalised data here, so 0-1
# Cold ratings: simulation
w_dr_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.40,1), sd=.05)
w_pc_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.30,1), sd=.05)
a_dr_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.1:.60,1), sd=.05)
a_pc_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.75,1), sd=.05)
w_dr_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.95,1), sd=.1)
w_pc_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.80,1), sd=.1)
a_dr_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.1)
a_pc_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.25:.95,1), sd=.1)

# Warm ratigs: simulation
w_dr_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.70,1), sd=.20)
w_pc_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.70,1), sd=.20)
a_dr_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.95,1), sd=.15)
a_pc_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.60,1), sd=.15)
w_dr_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
w_pc_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
a_dr_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
a_pc_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)

# Burning ratings: simulation
 w_dr_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.10)
 w_pc_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.70,1), sd=.15)
 a_dr_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.25:.95,1), sd=.10)
 a_pc_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.10)
 w_dr_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
 w_pc_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
 a_dr_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
 a_pc_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)

@@

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:60) {
  df <- simulate_subj(i, 0, 1)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

## H1
names(within)[7] <- 'within'
names(across)[7] <- 'across'
# merge
H1_df <- merge(within, across, by = c('id','cold_location','stimuli','quality'))
# difference
H1_df$diff <- H1_df$within - H1_df$across
# ttest
H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)
# effect size
H1es <- (mean(H1_df$diff))/(sd(H1_df$diff))
H1test
H1es
